Field training 02 - Leaf traits measurements

### 2023-07-18 submission_2/submission_2.qmd
Update submission_2.qmd

We further compared our LMA values with those from the LEDA database (See Figure 2 in this section). There, the values were available as mean SLA, so we converted them into LMA first (LMA = \frac{1}{SLA}). If several values were available for one plant species, we calculated the mean value. For two species (*Philadelphus Coronarius* and *Spirae Chamaedryfolia*) no values were available in the LEDA database. Overall, our values are slightly higher than those in the database, but generally similar (see Table 2 and Figure 2). Reasons for this may be inaccuracies in our sheet size script or inaccuracies in the sampling of the leaves by the respective processor (our group or people recorded in the LEDA database).

@@

>>>>

We further compared our LMA values with those from the LEDA database (See Figure 2 in this section). There, the values were available as mean SLA, so we converted them into LMA first ($LMA = \frac{1}{SLA}$). If several values were available for one plant species, we calculated the mean value. For two species (*Philadelphus Coronarius* and *Spirae Chamaedryfolia*) no values were available in the LEDA database. Overall, our values are slightly higher than those in the database, but generally similar (see Table 2 and Figure 2). Reasons for this may be inaccuracies in our sheet size script or inaccuracies in the sampling of the leaves by the respective processor (our group or people recorded in the LEDA database).

@@

Another task was to compare our LMA values with those from the LEDA database. There, the values were only available as SLA. So we had to convert them into LMA first. The result can be seen in the plots in the appendix. If several values were available for one plant, we calculated the mean value. For two plants no values were available in the LEDA database. Overall, our values are slightly higher than those in the database, but are very similar overall.
